---
title: "Explore data types in R"
author: "NguyenHo"
date: "2025-01-27"
output: html_document
---

# R Data Types

* numeric: This type of data is used to represent real numbers (including decimal numbers).

* logical: The logical data type represents the correct value (true) or false (false). This type of data is often used in comparisons and conditions.

* complex: Used to store complex numbers, somewhat real and virtual. Ex: 2 + 3i

* integer: Used to represent integers. You can create an integer by adding a quail L to a number.Ex: 5L

* character: Used to store characters (text). The string is placed in a double click (") or a single blink (').

* raw: The raw data type is used to store binary data. This data is rarely used in normal practice and is often used in advanced tasks such as low -level data processing.


```{r}
numeric<-c(12,2.50,-255,-24)
print(numeric)
```
```{r}
class(numeric)
```


```{r}
my_integer<-54L
print(my_integer)
```


```{r}
class(my_integer)

```


```
complex<-TRUE,FALSE
print(complex)

#ouput: Error: unexpected ',' in "complex<-TRUE,"
```


```{r}
class(complex)
```


```{r}
character<-c("hi","a")
print(character)

```


```{r}
class(character)
```


```{r}
typeof(character)
```


```{r}
int<-15
print(typeof(int))
```


```{r}
class(int)
```


```{r}
typeof(int)
```


```{r}
x=as.integer(int)
print(x)
```


```{r}
class(x)
```

```{r}
logi<-TRUE
class(logi)
```


```{r}
chracter<-"jdjdjdvbkjvb"
class(character)
```
