---
title: "learn how to write the first program in R"
author: "NguyenHo"
date: "2025-01-27"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# r is case sensitive
```{r}
print("Hello world!")
```


```{r}
plot(cars)
```
Add a new section by clicking the Insert Section button on the toolbar or by pressing Command+Option+I. 

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the Preview button or press Command+Shift+K to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
print("This is the first program.")
```


```{r}
x <- 10
y <- 20
z <- x + y
print(z)
```


```{r}
sum <- 11 + 12 - 13
print(sum)
```


```{r}
text <- "This is R program and I love programming."
print(text)
```


```{r}
squence <- 1:10
```


```{r}
print(squence)
```
